Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2022-04-16 doc/manuscript/ESSDmanuscript.Rmd
describe new variables

#Statistics
n_records_ForC= NA # total n records in ForC
n_plots_ForC = NA # total n plots in ForC
n_areas_ForC = NA # total n geographic areas in ForC
n_independent_records_ForC= NA #suspected duplicates removed
n_records_EFDB_variables= NA #n independent records relevant to EFDB
n_records_sent_to_EFDB = NA # n records sent to EFDB
n_records_posted_EFDB = NA # n records accepted and posted in EFDB
```

@@

Previous versions of ForC [@refs] contained most of the information required for transfer to EFDB, and, more broadly, to inform C accounting under IPCC guidelines. 
However, modest changes to the structure and contents of ForC were needed in order to provide all information fequired by EFDB and to improve ForC's capacity to serve as a repository of valuable information for forest C accounting under IPCC guidelines.
To support export of data to EFDB, and to improve the overall quality of the ForC database, we added or modified ## fields (Table ##), defined ## new variables, implemented enhanced quality control, manually reviewed ># records to obtain additional required information, and added # new records.

@@

We added eleven increment variables to the set of named and defined variables (or 22, counting _OM and _C versions), which previously included only one (aboveground biomass increment, *delta.agb*). 
*(https://github.com/forc-db/IPCC-EFDB-integration/issues/6)*
These are directly related to C stocks as previously defined in ForC, with "*delta.*" added in front of the variable name.

Although these variables currently lack records, the structure exists such that records can be populated over time.

To provide better definition of the previously existing variable *organic.layer*, which has a nebulous definition that reflects the varied definitions adopted by original studies, we added two clearly defined variables: *litter* (relatively undecomposed plant material/ OL horizon), and *O.horizon* (entire O-horizon, including *litter* (OL)).

>>>>

#Statistics
n_records_ForC= NA # total n records in ForC
n_plots_ForC = NA # total n plots in ForC
n_areas_ForC = NA # total n geographic areas in ForC
n_independent_records_ForC= NA #suspected duplicates removed
n_records_EFDB_variables= NA #n independent records relevant to EFDB
n_records_sent_to_EFDB = NA # n records sent to EFDB
n_records_posted_EFDB = NA # n records accepted and posted in EFDB

n_new_variables = 11 + 2 + 2 #delta. + woody.mortality + O horizon
```

@@

Previous versions of ForC [@refs] contained most of the information required for transfer to EFDB, and, more broadly, to inform C accounting under IPCC guidelines. 
However, modest changes to the structure and contents of ForC were needed in order to provide all information required by EFDB and to improve ForC's capacity to serve as a repository of valuable information for forest C accounting under IPCC guidelines.
To support export of data to EFDB, and to improve the overall quality of the ForC database, we added or modified ## fields (Table ##), defined `r n_new_variables` new variables, implemented enhanced quality control, manually reviewed ># records to obtain additional required information, and added # new records.

@@

We added a total of `r n_new_variables` new variables to the set of named and defined variables, counting each pair of variables with units in C (ending in  `_C`) or organic matter (ending in `_OM`) as one. 
All of these variables are relevant to C accounting under IPCC, and hence to EFDB (Fig. `r fig_variable_mapping`)
This included eleven increment variables, adding to only one previously defined increment variable (aboveground biomass increment, *delta.agb*). 
These are directly related to C stocks as previously defined in ForC, with "*delta.*" added in front of the variable name.
Further, we added variables capturing the belowground component of woody mortality (*woody.mortality_root*) and the combined aboveground and belowground components of woody mortality (*woody.mortality*).
Although most of these variables currently lack records in ForC, the structure exists such that records can be populated over time.

Further, to provide better definition of the previously existing variable *organic.layer*, which has a nebulous definition that reflects the varied definitions adopted by original studies, we added two clearly defined variables: *litter* (relatively undecomposed plant material/ OL horizon), and *O.horizon* (entire O-horizon, including *litter* (OL)).

### 2022-04-16 doc/manuscript/ESSDmanuscript.tex
describe new variables

Previous versions of ForC \citep{refs} contained most of the information
required for transfer to EFDB, and, more broadly, to inform C accounting
under IPCC guidelines. However, modest changes to the structure and
contents of ForC were needed in order to provide all information
fequired by EFDB and to improve ForC's capacity to serve as a repository
of valuable information for forest C accounting under IPCC guidelines.
To support export of data to EFDB, and to improve the overall quality of
the ForC database, we added or modified \#\# fields (Table \#\#),
defined \#\# new variables, implemented enhanced quality control,
manually reviewed \textgreater\# records to obtain additional required
information, and added \# new records.

@@

We added eleven increment variables to the set of named and defined
variables (or 22, counting \_OM and \_C versions), which previously
included only one (aboveground biomass increment, \emph{delta.agb}).
\emph{(https://github.com/forc-db/IPCC-EFDB-integration/issues/6)} These
are directly related to C stocks as previously defined in ForC, with
``\emph{delta.}'' added in front of the variable name.

Although these variables currently lack records, the structure exists
such that records can be populated over time.

To provide better definition of the previously existing variable
\emph{organic.layer}, which has a nebulous definition that reflects the
varied definitions adopted by original studies, we added two clearly
defined variables: \emph{litter} (relatively undecomposed plant
material/ OL horizon), and \emph{O.horizon} (entire O-horizon, including
\emph{litter} (OL)).

>>>>

Previous versions of ForC \citep{refs} contained most of the information
required for transfer to EFDB, and, more broadly, to inform C accounting
under IPCC guidelines. However, modest changes to the structure and
contents of ForC were needed in order to provide all information
required by EFDB and to improve ForC's capacity to serve as a repository
of valuable information for forest C accounting under IPCC guidelines.
To support export of data to EFDB, and to improve the overall quality of
the ForC database, we added or modified \#\# fields (Table \#\#),
defined 15 new variables, implemented enhanced quality control, manually
reviewed \textgreater\# records to obtain additional required
information, and added \# new records.

@@

We added a total of 15 new variables to the set of named and defined
variables, counting each pair of variables with units in C (ending in
\texttt{\_C}) or organic matter (ending in \texttt{\_OM}) as one. All of
these variables are relevant to C accounting under IPCC, and hence to
EFDB (Fig. 1) This included eleven increment variables, adding to only
one previously defined increment variable (aboveground biomass
increment, \emph{delta.agb}). These are directly related to C stocks as
previously defined in ForC, with ``\emph{delta.}'' added in front of the
variable name. Further, we added variables capturing the belowground
component of woody mortality (\emph{woody.mortality\_root}) and the
combined aboveground and belowground components of woody mortality
(\emph{woody.mortality}). Although most of these variables currently
lack records in ForC, the structure exists such that records can be
populated over time.

Further, to provide better definition of the previously existing
variable \emph{organic.layer}, which has a nebulous definition that
reflects the varied definitions adopted by original studies, we added
two clearly defined variables: \emph{litter} (relatively undecomposed
plant material/ OL horizon), and \emph{O.horizon} (entire O-horizon,
including \emph{litter} (OL)).
